WIDS 2024 Final Presentation

### 2024-01-12 Documents/Presentation.qmd
populated presentation

## Data manipulation pt. 1

@@

## Data Manipulation pt. 2

@@

## EDA pt. 1: Overview

-   EDA was split into five sections: wage data, union data, house data, wage data's associations with union data, and union data's association with house data. We did not have the relevent wage data to compare wages and house elections

## EDA pt. 2: Wage Data

::: columns
::: {.column width="60%"}
-   Minimum wages, which had been stagnant since 2009, began to grow again in 2016, although the federal rate has remained stagnant
-   Incomes, when adjusted for inflation, have been decreasing since 1984. Surprisingly, our data shows income inequality has remained stagnant over the last forty years.
:::

::: {.column width="40%"}

@@

## EDA pt. 3: Union Data

::: {.column width="40%"}
column 2
:::
:::

## EDA pt. 4: House Data

::: columns
::: {.column width="60%"}
-   The country has generally grown more republican in the last 40 years, although data in the last 10 years show the pendulem might now be swinging the other way
    -   Northern-midwest states have had the biggest shift to the right. New England is the only region that has seen a shift left.
:::

::: {.column width="40%"}
column 2
:::
:::

## EDA pt. 5: Wage Data's Interactions With Union Data

::: {.column width="40%"}
column 2
:::
:::

## EDA pt. 6: House Election Data's Interactions With Union Data

::: columns
::: {.column width="60%"}
-   Unions have become a very political topic in the last 40 years
-   This trend appears to be driven by the northeast and south
:::

::: {.column width="40%"}
column 2
:::
:::

## Models

## Conclusion

## Where we would take our project in the future

##

>>>>

## Data manipulation pt. 1 {.smaller}

@@

## Data manipulation pt. 2 {.smaller}

@@

## EDA pt. 1: Overview {.smaller}

-   EDA was split into five sections: wage data, union data, house data, wage data's associations with union data, and union data's association with house data. We did not have the relevant wage data to compare wages and house elections

## EDA pt. 2: Wage Data {.smaller}

::: columns
::: {.column width="60%"}
-   Incomes, when adjusted for inflation, have been decreasing since 1984. Surprisingly, our data shows income inequality has remained stagnant over the last forty years.
-   Minimum wages, which had been stagnant since 2009, began to grow again in 2016, although the federal rate has remained stagnant
:::

::: {.column width="40%"}
![Plot 1](./Graph_Images/Income_by_year_adj.png)
![Plot 2](./Graph_Images/Eff_wage_by_state.png)
:::
:::

## EDA pt. 3: Union Data {.smaller}

::: {.column width="40%"}
![Plot 3](./Graph_Images/States_by_CB.png)
:::
:::

## EDA pt. 4: House Data {.smaller}

::: columns
::: {.column width="60%"}
-   The country has generally grown more republican in the last 40 years, although data in the last 10 years show the pendulum might now be swinging the other way
    -   Northern-midwest states have had the biggest shift to the right. New England is the only region that has seen a shift left.
:::

::: {.column width="40%"}
![Plot 4](./Graph_Images/House_by_year.png)
:::
:::

## EDA pt. 5: Wage Data's Interactions With Union Data {.smaller}

::: {.column width="40%"}
![Plot 5](./Graph_Images/Union_wage_by_decade.png)
:::
:::

## EDA pt. 6: House Election Data's Interactions With Union Data {.smaller}

::: columns
::: {.column width="60%"}
-   Unions have become a very political topic in the last 40 years
-   This trend appears to be driven by the north central and south regions.
:::

::: {.column width="40%"}
![Plot 6](./Graph_Images/CB_by_decade1.png)
![Plot 7](./Graph_Images/CB_by_decade2.png)

@@

## Models {.smaller}
::: columns
::: {.column width="60%"}
-   Regression
- T-test between union and non union wages
  - 1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
    - mean of x = 26.306;  mean of y = 20.375
    - 95% CI: (5.347, 6.514)
  - 2010s: t = 22.846, df = 9.4096, p-value = 1.462e-09
    - mean of x = 3.786;  mean of y = 25.664
    - 95% CI: (3.786, 5.952)
:::

::: {.column width="40%"}
![Plot 8](./Graph_Images/Regression_plot.png)

## Conclusion {.smaller}

## Where we would take our project in the future {.smaller}

# Thank You

## Bibliography {.smaller}
